### 2023-02-27 doc/university-covid.tex
finalize

\begin{figure}[!th]
\includegraphics[width=0.95\textwidth]{../figure_princeton_new/figure_princeton_new_per_1000.pdf}
\caption{
\textbf{Dynamics of SARS-CoV-2 outbreaks in Princeton University (PU).}
(A--D) Epidemic trajectories across four semesters: Fall 2020--2021 (A), Spring 2020--2021 (B), Fall 2021--2022 (C), and Spring 2021--2022 (D).
Colored bar plots represent the weekly number of cases per 1000 from both asymptomatic and symptomatic testing in PU.
Red lines represent the weekly number of cases per 1000 in Mercer County.
Number of cases in Mercer County is obtained from \url{https://github.com/nytimes/covid-19-data}.
The weekly number of cases per 1000 in Princeton is normalized by the approximate total size of the PU population present on campus for each semester: 3000 for Fall 2020--2021, 8000 for Spring 2020--2021, 13000 for Fall 2021--2022, and 15000 for Spring 2021--2022.
The weekly number of cases per 1000 in Princeton in Mercer County is calculated based on the total population size as of 2020: 387340 (\url{www.census.gov}).
(E--H) Correlations between the weekly number of cases per 1000 in PU and in Mercer County.
Solid lines and shaded areas represent the estimated linear regression lines and the associated 95\% CIs.
(I--L) Ratios between weekly number of cases per 1000 in PU and Mercer County.
The dashed lines represent the 1:1 ratio.
\label{fig:princeton}
}
\end{figure}

@@

\begin{figure}[!th]
\includegraphics[width=\textwidth]{../figure_princeton_new/figure_princeton_simulation.pdf}
\caption{
\textbf{Retrospective analysis of past SARS-CoV-2 outbreaks on Princeton University (PU) campus.}
(A, D, G) Time series comparisons of model predictions with observed data across ranges of contact reproduction number $\Rc$ and scaling parameter for community contact $\theta$.
For each parameter combination, we simulate the model 100 times and calculate the sum of squared differences (SSQ) between the reported number of positive cases and the model-predicted number of positive cases. 
Heat maps represent medians of the logged sum of squared differences.
Circles represent the best fitting parameter set.
(B, E, H) Model predictions. 
Solid lines represent median predictions.
Dashed lines represent a realization with the least sum of squared errors.
Shaded areas represent 90\% quantiles for the best matching parameter set.
Points represent the observed data.
(C, F, I) Correlations between model predictions with observed data.
Colored solid lines and shaded areas represent the estimated linear regression lines and the associated 95\% CIs.
Dashed lines represent the one-to-one line.
\label{fig:matching}
}
\end{figure}

@@

\begin{figure}[!ht]
\includegraphics[width=\textwidth]{../figure_princeton_new/figure_princeton_simulation_omicron_spring.pdf}
\caption{
\textbf{The impact of changes in testing frequency and an increased reproduction number on the spread of the Omicron variant.}
Solid lines represent median predictions.
Shaded areas represent 90\% quantiles across 100 simulations.
Points represent the observed data.
Vertical dashed lines represent the week including February 8, 2022, when distancing and testing policies were updated on PU campus.
For each row, we assume a fixed value of baseline contact reproduction number $\Rc$ ranging from 2 to 6 across rows.
Then, we simulate increase in $\Rc$ at the time of policy change (indicated by column labels).
}
\label{fig:omicron1}
\end{figure}

@@

\begin{figure}[!thp]
\includegraphics[width=\textwidth]{../figure_princeton_new/figure_princeton_simulation_omicron_outbreak.pdf}
\caption{
\textbf{The impact of large super spreading events on the spread of the Omicron variant.}
Solid lines represent median predictions.
Shaded areas represent 90\% quantiles across 100 simulations.
Points represent the observed data.
Vertical dashed lines represent the week including February 8, 2022, when distancing and testing policies were updated on PU campus.
}
\label{fig:omicron2}
\end{figure}

@@

\bibliography{university-covid}

\section*{Supplementary Figures}

\renewcommand{\thefigure}{S\arabic{figure}}
\setcounter{figure}{0}

\begin{figure}[!htp]
\includegraphics[width=0.9\textwidth]{../figure_princeton_new/figure_princeton_testing.pdf}
\caption{
\textbf{The weekly number of PCR tests stratified by subpopulations.}
}
\end{figure}

\begin{figure}[!htp]
\includegraphics[width=\textwidth]{../figure_princeton_new/figure_princeton_new_per_1000_bypop.pdf}
\caption{
\textbf{The weekly number of cases per 1000 stratified by subpopulations.}
The case trajectory for undergraduate students was omitted for the fall semester of 2020--2021 academic year due to a very low number of undergraduate students present on campus.
}
\end{figure}

\begin{figure}[!htp]
\includegraphics[width=\textwidth]{../figure_princeton_new/figure_princeton_correlation_per_1000.pdf}
\caption{
\textbf{Correlations between the weekly number of cases in PU and in Mercer County stratified by subpopulations.}
Points represent the number of reported cases.
Solid lines and shaded areas represent the regression line and the associated 95\% confidence intervals.
}
\end{figure}

\begin{figure}[!htp]
\begin{center}
\includegraphics[width=\textwidth]{../figure_princeton_new/figure_princeton_map_new.pdf}
\end{center}
\caption{
\textbf{Correlations between the weekly number of cases in PU and in counties in New Jersey.}
(A--C) Map of correlations between the weekly number of cases in PU and in counties in New Jersey.
(D--F) Relationship between case correlations and distance from Mercer County.
Points represent the estimated correlation coefficients.
Solid lines and shaded areas represent the regression line and the associated 95\% confidence intervals.
Black points and lines represent correlations based on all cases in PU.
Red points and lines represent correlations based on cases among faculty and staff members in PU.
}
\end{figure}

\begin{figure}[!htp]
\includegraphics[width=\textwidth]{../figure_princeton_new/figure_princeton_newyork_new.pdf}
\caption{
\textbf{Dynamics of SARS-CoV-2 outbreaks in PU and New York City.}
(A--C) Epidemic trajectories across three semesters: Fall 2020 (A), Spring 2020 (B), and Fall 20201 (C).
Colored bar plots represent the weekly number of cases from both asymptomatic and symptomatic testing in PU.
Red lines represent the weekly number of cases in New York City.
(D--F) Correlations between the weekly number of cases in PU and in New York City.
Solid lines and shaded areas represent the estimated linear regression lines and the associated 95\% CIs.
}
\end{figure}

\begin{figure}[!htp]
\includegraphics[width=\textwidth]{../figure_princeton_new/figure_princeton_philly_new.pdf}
\caption{
\textbf{Dynamics of SARS-CoV-2 outbreaks in PU and Philadelphia.}
(A--C) Epidemic trajectories across three semesters: Fall 2020 (A), Spring 2020 (B), and Fall 20201 (C).
Colored bar plots represent the weekly number of cases from both asymptomatic and symptomatic testing in PU.
Red lines represent the weekly number of cases in Philadelphia.
(D--F) Correlations between the weekly number of cases in PU and in Philadelphia.
Solid lines and shaded areas represent the estimated linear regression lines and the associated 95\% CIs.
}
\end{figure}

\begin{figure}[!htp]
\includegraphics[width=0.8\textwidth]{../figure_princeton_new/figure_princeton_map_extended.pdf}
\caption{
\textbf{Correlations between the weekly number of cases in PU and in counties in New Jersey, Pennsylvania, and New York State.}
(A--C) Map of correlations between the weekly number of cases in PU and in counties in New Jersey, Pennsylvania, and New York State.
(D--F) Relationship between case correlations and distance from Mercer County.
Points represent the estimated correlation coefficients.
Solid lines and shaded areas represent the regression line and the associated 95\% confidence intervals.
Black points and lines represent correlations based on all cases in PU.
Red points and lines represent correlations based on cases among faculty and staff members in PU.
New York City is excluded from this analysis as the data provided by New York Times are not further stratified by county levels.
}
\end{figure}

\begin{figure}[!htp]
\includegraphics[width=\textwidth]{../figure_diagram/diagram.pdf}
\caption{
\textbf{Compartmental diagram of the individual-based model.}
Each compartment represents a stage of infection: susceptible $S$, exposed $S$, pre-symptomatic $I_p$, symptomatic $I_s$, asymptomatic $I_a$, and recovered $R$.
Pre-symptomatic, symptomatic, and asymptomatic stages are further divided into two subcompartments.
Individuals in pre-symptomatic, symptomatic, and asymptomatic stages can test positive with 95\% sensitivity.
}
\end{figure}

\begin{figure}[!htp]
\includegraphics[width=\textwidth]{../figure_princeton_new/figure_princeton_simulation_fall_2020_all.pdf}
\caption{
\textbf{Comparisons between model predictions and the observed numbers of cases for fall 2020.}
Points represent the weekly number of reported cases in PU.
Red lines and shaded areas represent median model predictions and 90\% quantiles across 100 simulations.
See figure 2 in the main text for details.
}
\end{figure}

\begin{figure}[!htp]
\includegraphics[width=\textwidth]{../figure_princeton_new/figure_princeton_simulation_spring_2020_all.pdf}
\caption{
\textbf{Comparisons between model predictions and the observed numbers of cases for spring 2020.}
Points represent the weekly number of reported cases in PU.
Red lines and shaded areas represent median model predictions and 90\% quantiles across 100 simulations.
See figure 2 in the main text for details.
}
\end{figure}

\begin{figure}[!htp]
\includegraphics[width=\textwidth]{../figure_princeton_new/figure_princeton_simulation_fall_2021_all.pdf}
\caption{
\textbf{Comparisons between model predictions and the observed numbers of cases for fall 2021.}
Points represent the weekly number of reported cases in PU.
Red lines and shaded areas represent median model predictions and 90\% quantiles across 100 simulations.
See figure 2 in the main text for details.
}
\end{figure}

\begin{figure}[!htp]
\includegraphics[width=\textwidth]{../figure_princeton_new/figure_princeton_simulation_nowaning.pdf}
\caption{
\textbf{Comparisons between model predictions and the observed numbers of cases for fall 2021 without immunity waning.}
Points represent the weekly number of reported cases in PU.
Red lines and shaded areas represent median model predictions and 90\% quantiles across 100 simulations.
See figure 2 in the main text for details.
}
\end{figure}

\begin{figure}[!htp]
\includegraphics[width=\textwidth]{../figure_princeton_new/figure_princeton_simulation_omicron_spring_shortI.pdf}
\caption{
\textbf{The impact of changes in testing frequency and an increased reproduction number on the spread of the Omicron variant, assuming a shorter latent and infectious periods.}
Solid lines represent median predictions.
Shaded areas represent 90\% quantiles across 100 simulations.
Points represent the observed data.
Vertical dashed lines represent the week including February 8, 2022, when distancing and testing policies were updated on PU campus.
For each row, we assume a fixed value of baseline contact reproduction number $\Rc$ ranging from 2 to 6 across rows.
Then, we simulate increase in $\Rc$ at the time of policy change (indicated by column labels).
Here, the assumed mean latent, presymptomatic, and asymptomatic stages of infection are 0.5 days shorter than the assumed values for simulations presented in Figure 3 in the main text.
}
\end{figure}

\begin{figure}[!htp]
\includegraphics[width=\textwidth]{../figure_princeton_new/figure_princeton_simulation_omicron_spring_shortI.pdf}
\caption{
\textbf{The impact of changes in testing frequency and an increased reproduction number on the spread of the Omicron variant, assuming a lower vaccine effectiveness.}
Solid lines represent median predictions.
Shaded areas represent 90\% quantiles across 100 simulations.
Points represent the observed data.
Vertical dashed lines represent the week including February 8, 2022, when distancing and testing policies were updated on PU campus.
For each row, we assume a fixed value of baseline contact reproduction number $\Rc$ ranging from 2 to 6 across rows.
Then, we simulate increase in $\Rc$ at the time of policy change (indicated by column labels).
Here, we assume 30\% vaccine effectiveness against infection.
}
\end{figure}

>>>>

\begin{figure}[!th]
\includegraphics[width=0.95\textwidth]{figure_princeton_new_per_1000.pdf}
\caption{
\textbf{Dynamics of SARS-CoV-2 outbreaks in Princeton University (PU).}
(A--D) Epidemic trajectories across four semesters: Fall 2020--2021 (A), Spring 2020--2021 (B), Fall 2021--2022 (C), and Spring 2021--2022 (D).
Colored bar plots represent the weekly number of cases per 1000 from both asymptomatic and symptomatic testing in PU.
Red lines represent the weekly number of cases per 1000 in Mercer County.
Number of cases in Mercer County is obtained from \url{https://github.com/nytimes/covid-19-data}.
The weekly number of cases per 1000 in Princeton is normalized by the approximate total size of the PU population present on campus for each semester: 3000 for Fall 2020--2021, 8000 for Spring 2020--2021, 13000 for Fall 2021--2022, and 15000 for Spring 2021--2022.
The weekly number of cases per 1000 in Princeton in Mercer County is calculated based on the total population size as of 2020: 387340 (\url{www.census.gov}).
(E--H) Correlations between the weekly number of cases per 1000 in PU and in Mercer County.
Solid lines and shaded areas represent the estimated linear regression lines and the associated 95\% CIs.
(I--L) Ratios between weekly number of cases per 1000 in PU and Mercer County.
The dashed lines represent the 1:1 ratio.
\label{fig:princeton}
}
\end{figure}

@@

\begin{figure}[!th]
\includegraphics[width=\textwidth]{figure_princeton_simulation.pdf}
\caption{
\textbf{Retrospective analysis of past SARS-CoV-2 outbreaks on Princeton University (PU) campus.}
(A, D, G) Time series comparisons of model predictions with observed data across ranges of contact reproduction number $\Rc$ and scaling parameter for community contact $\theta$.
For each parameter combination, we simulate the model 100 times and calculate the sum of squared differences (SSQ) between the reported number of positive cases and the model-predicted number of positive cases. 
Heat maps represent medians of the logged sum of squared differences.
Circles represent the best fitting parameter set.
(B, E, H) Model predictions. 
Solid lines represent median predictions.
Dashed lines represent a realization with the least sum of squared errors.
Shaded areas represent 90\% quantiles for the best matching parameter set.
Points represent the observed data.
(C, F, I) Correlations between model predictions with observed data.
Colored solid lines and shaded areas represent the estimated linear regression lines and the associated 95\% CIs.
Dashed lines represent the one-to-one line.
\label{fig:matching}
}
\end{figure}

@@

\begin{figure}[!ht]
\includegraphics[width=\textwidth]{figure_princeton_simulation_omicron_spring.pdf}
\caption{
\textbf{The impact of changes in testing frequency and an increased reproduction number on the spread of the Omicron variant.}
Solid lines represent median predictions.
Shaded areas represent 90\% quantiles across 100 simulations.
Points represent the observed data.
Vertical dashed lines represent the week including February 8, 2022, when distancing and testing policies were updated on PU campus.
For each row, we assume a fixed value of baseline contact reproduction number $\Rc$ ranging from 2 to 6 across rows.
Then, we simulate increase in $\Rc$ at the time of policy change (indicated by column labels).
}
\label{fig:omicron1}
\end{figure}

@@

\begin{figure}[!thp]
\includegraphics[width=\textwidth]{figure_princeton_simulation_omicron_outbreak.pdf}
\caption{
\textbf{The impact of large super spreading events on the spread of the Omicron variant.}
Solid lines represent median predictions.
Shaded areas represent 90\% quantiles across 100 simulations.
Points represent the observed data.
Vertical dashed lines represent the week including February 8, 2022, when distancing and testing policies were updated on PU campus.
}
\label{fig:omicron2}
\end{figure}

@@

\section*{Author contribution}

All authors contributed equally to the research design, data collection, formal analysis, interpretation of the results, and writing of the paper.

\begin{thebibliography}{}

\bibitem[\protect\citeauthoryear{Baker, Mahmud, Wagner, Yang, Pitzer, Viboud,
  Vecchi, Metcalf, and Grenfell}{Baker et~al.}{2019}]{baker2019epidemic}
Baker, R.~E., A.~S. Mahmud, C.~E. Wagner, W.~Yang, V.~E. Pitzer, C.~Viboud,
  G.~A. Vecchi, C.~J.~E. Metcalf, and B.~T. Grenfell (2019).
\newblock Epidemic dynamics of respiratory syncytial virus in current and
  future climates.
\newblock {\em Nature communications\/}~{\em 10\/}(1), 1--8.

\bibitem[\protect\citeauthoryear{Baker, Park, Wagner, and Metcalf}{Baker
  et~al.}{2021}]{baker2021limits}
Baker, R.~E., S.~W. Park, C.~E. Wagner, and C.~J.~E. Metcalf (2021).
\newblock {The limits of SARS-CoV-2 predictability}.
\newblock {\em Nature Ecology \& Evolution\/}~{\em 5\/}(8), 1052--1054.

\bibitem[\protect\citeauthoryear{Brett and Rohani}{Brett and
  Rohani}{2020}]{brett2020transmission}
Brett, T.~S. and P.~Rohani (2020).
\newblock {Transmission dynamics reveal the impracticality of COVID-19 herd
  immunity strategies}.
\newblock {\em Proceedings of the National Academy of Sciences\/}~{\em
  117\/}(41), 25897--25903.

\bibitem[\protect\citeauthoryear{Brook, Northrup, Ehrenberg, Doudna, Boots,
  Consortium, et~al.}{Brook et~al.}{2021}]{brook2021optimizing}
Brook, C.~E., G.~R. Northrup, A.~J. Ehrenberg, J.~A. Doudna, M.~Boots,
  I.~S.-C.-.~T. Consortium, et~al. (2021).
\newblock {Optimizing COVID-19 control with asymptomatic surveillance testing
  in a university environment}.
\newblock {\em Epidemics\/}~{\em 37}, 100527.

\bibitem[\protect\citeauthoryear{Cobey}{Cobey}{2020}]{cobey2020modeling}
Cobey, S. (2020).
\newblock Modeling infectious disease dynamics.
\newblock {\em Science\/}~{\em 368\/}(6492), 713--714.

\bibitem[\protect\citeauthoryear{Currie, Moreno, Delahoy, Pray, Jovaag, Braun,
  Cole, Shechter, Fajardo, Griggs, et~al.}{Currie
  et~al.}{2021}]{currie2021interventions}
Currie, D.~W., G.~K. Moreno, M.~J. Delahoy, I.~W. Pray, A.~Jovaag, K.~M. Braun,
  D.~Cole, T.~Shechter, G.~C. Fajardo, C.~Griggs, et~al. (2021).
\newblock {Interventions to Disrupt Coronavirus Disease Transmission at a
  University, Wisconsin, USA, August--October 2020}.
\newblock {\em Emerging infectious diseases\/}~{\em 27\/}(11), 2776.

\bibitem[\protect\citeauthoryear{{Duke University}}{{Duke
  University}}{2021}]{dukeoutbreak}
{Duke University} (2021).
\newblock {Important COVID updates for undergrads, Aug. 30}.

\bibitem[\protect\citeauthoryear{Elderd, Dukic, and Dwyer}{Elderd
  et~al.}{2006}]{elderd2006uncertainty}
Elderd, B.~D., V.~M. Dukic, and G.~Dwyer (2006).
\newblock Uncertainty in predictions of disease spread and public health
  responses to bioterrorism and emerging diseases.
\newblock {\em Proceedings of the National Academy of Sciences\/}~{\em
  103\/}(42), 15693--15697.

\bibitem[\protect\citeauthoryear{Endo, {Centre for the Mathematical Modelling
  of Infectious Diseases COVID-19 Working Group}, Abbott, Kucharski, and
  Funk}{Endo et~al.}{2020}]{10.12688/wellcomeopenres.15842.3}
Endo, A., {Centre for the Mathematical Modelling of Infectious Diseases
  COVID-19 Working Group}, S.~Abbott, A.~Kucharski, and S.~Funk (2020).
\newblock {Estimating the overdispersion in COVID-19 transmission using
  outbreak sizes outside China [version 3; peer review: 2 approved]}.
\newblock {\em Wellcome Open Research\/}~{\em 5\/}(67).

\bibitem[\protect\citeauthoryear{Ferguson, Ghani, Cori, Hogan, Hinsley, and
  Volz}{Ferguson et~al.}{2021}]{ferguson2021report}
Ferguson, N., A.~Ghani, A.~Cori, A.~Hogan, W.~Hinsley, and E.~Volz (2021).
\newblock {Report 49: Growth, population distribution and immune escape of
  Omicron in England}.

\bibitem[\protect\citeauthoryear{Flaxman, Mishra, Gandy, Unwin, Mellan,
  Coupland, Whittaker, Zhu, Berah, Eaton, et~al.}{Flaxman
  et~al.}{2020}]{flaxman2020estimating}
Flaxman, S., S.~Mishra, A.~Gandy, H.~J.~T. Unwin, T.~A. Mellan, H.~Coupland,
  C.~Whittaker, H.~Zhu, T.~Berah, J.~W. Eaton, et~al. (2020).
\newblock {Estimating the effects of non-pharmaceutical interventions on
  COVID-19 in Europe}.
\newblock {\em Nature\/}~{\em 584\/}(7820), 257--261.

\bibitem[\protect\citeauthoryear{Fox, Bailey, Seamon, and Miranda}{Fox
  et~al.}{2021}]{fox2021response}
Fox, M.~D., D.~C. Bailey, M.~D. Seamon, and M.~L. Miranda (2021).
\newblock {Response to a COVID-19 outbreak on a university campus—Indiana,
  August 2020}.
\newblock {\em Morbidity and Mortality Weekly Report\/}~{\em 70\/}(4), 118.

\bibitem[\protect\citeauthoryear{Frazier, Cashore, Duan, Henderson, Janmohamed,
  Liu, Shmoys, Wan, and Zhang}{Frazier et~al.}{2022}]{frazier2022modeling}
Frazier, P.~I., J.~M. Cashore, N.~Duan, S.~G. Henderson, A.~Janmohamed, B.~Liu,
  D.~B. Shmoys, J.~Wan, and Y.~Zhang (2022).
\newblock {Modeling for COVID-19 college reopening decisions: Cornell, a case
  study}.
\newblock {\em Proceedings of the National Academy of Sciences\/}~{\em
  119\/}(2).

\bibitem[\protect\citeauthoryear{Galanti, Pei, Yamana, Angulo, Charos,
  Swerdlow, and Shaman}{Galanti et~al.}{2021}]{galanti2021social}
Galanti, M., S.~Pei, T.~K. Yamana, F.~J. Angulo, A.~Charos, D.~L. Swerdlow, and
  J.~Shaman (2021).
\newblock Social distancing remains key during vaccinations.
\newblock {\em Science\/}~{\em 371\/}(6528), 473--474.

\bibitem[\protect\citeauthoryear{Gibson, Weitz, Shannon, Holton, Bryksin, Liu,
  Sieglinger, Coenen, Zhao, Beckett, et~al.}{Gibson
  et~al.}{2021}]{gibson2021surveillance}
Gibson, G., J.~S. Weitz, M.~P. Shannon, B.~Holton, A.~Bryksin, B.~Liu,
  M.~Sieglinger, A.~R. Coenen, C.~Zhao, S.~J. Beckett, et~al. (2021).
\newblock {Surveillance-to-Diagnostic Testing Program for Asymptomatic
  SARS-CoV-2 Infections on a Large, Urban Campus in Fall 2020}.
\newblock {\em Epidemiology\/}~{\em 33\/}(2), 209--216.

\bibitem[\protect\citeauthoryear{Grenfell and Harwood}{Grenfell and
  Harwood}{1997}]{grenfell1997meta}
Grenfell, B. and J.~Harwood (1997).
\newblock (meta) population dynamics of infectious diseases.
\newblock {\em Trends in ecology \& evolution\/}~{\em 12\/}(10), 395--399.

\bibitem[\protect\citeauthoryear{Grenfell, Bj{\o}rnstad, and Kappey}{Grenfell
  et~al.}{2001}]{grenfell2001travelling}
Grenfell, B.~T., O.~N. Bj{\o}rnstad, and J.~Kappey (2001).
\newblock Travelling waves and spatial hierarchies in measles epidemics.
\newblock {\em Nature\/}~{\em 414\/}(6865), 716--723.

\bibitem[\protect\citeauthoryear{Hamer, White, Jenkins, Gill, Landsberg,
  Klapperich, Bulekova, Platt, Decarie, Gilmore, et~al.}{Hamer
  et~al.}{2021}]{hamer2021assessment}
Hamer, D.~H., L.~F. White, H.~E. Jenkins, C.~J. Gill, H.~E. Landsberg,
  C.~Klapperich, K.~Bulekova, J.~Platt, L.~Decarie, W.~Gilmore, et~al. (2021).
\newblock {Assessment of a COVID-19 control plan on an urban university campus
  during a second wave of the pandemic}.
\newblock {\em JAMA Network Open\/}~{\em 4\/}(6), e2116425--e2116425.

\bibitem[\protect\citeauthoryear{{Harvard University}}{{Harvard
  University}}{2021}]{harvardoutbreak}
{Harvard University} (2021).
\newblock {Increase in COVID-19 cases, Take Steps to Protect Yourself \& Our
  Community}.

\bibitem[\protect\citeauthoryear{He, Ionides, and King}{He
  et~al.}{2010}]{he2010plug}
He, D., E.~L. Ionides, and A.~A. King (2010).
\newblock Plug-and-play inference for disease dynamics: measles in large and
  small populations as a case study.
\newblock {\em Journal of the Royal Society Interface\/}~{\em 7\/}(43),
  271--283.

\bibitem[\protect\citeauthoryear{Hellewell, Abbott, Gimma, Bosse, Jarvis,
  Russell, Munday, Kucharski, Edmunds, Sun, et~al.}{Hellewell
  et~al.}{2020}]{hellewell2020feasibility}
Hellewell, J., S.~Abbott, A.~Gimma, N.~I. Bosse, C.~I. Jarvis, T.~W. Russell,
  J.~D. Munday, A.~J. Kucharski, W.~J. Edmunds, F.~Sun, et~al. (2020).
\newblock {Feasibility of controlling COVID-19 outbreaks by isolation of cases
  and contacts}.
\newblock {\em The Lancet Global Health\/}~{\em 8\/}(4), e488--e496.

\bibitem[\protect\citeauthoryear{Hellewell, Russell, Beale, Kelly, Houlihan,
  Nastouli, and Kucharski}{Hellewell et~al.}{2021}]{hellewell2021estimating}
Hellewell, J., T.~W. Russell, R.~Beale, G.~Kelly, C.~Houlihan, E.~Nastouli, and
  A.~J. Kucharski (2021).
\newblock {Estimating the effectiveness of routine asymptomatic PCR testing at
  different frequencies for the detection of SARS-CoV-2 infections}.
\newblock {\em BMC medicine\/}~{\em 19\/}(1), 1--10.

\bibitem[\protect\citeauthoryear{Holmdahl and Buckee}{Holmdahl and
  Buckee}{2020}]{holmdahl2020wrong}
Holmdahl, I. and C.~Buckee (2020).
\newblock {Wrong but useful—what COVID-19 epidemiologic models can and cannot
  tell us}.
\newblock {\em New England Journal of Medicine\/}~{\em 383\/}(4), 303--305.

\bibitem[\protect\citeauthoryear{Kissler, Tedijanto, Goldstein, Grad, and
  Lipsitch}{Kissler et~al.}{2020}]{kissler2020projecting}
Kissler, S.~M., C.~Tedijanto, E.~Goldstein, Y.~H. Grad, and M.~Lipsitch (2020).
\newblock {Projecting the transmission dynamics of SARS-CoV-2 through the
  postpandemic period}.
\newblock {\em Science\/}~{\em 368\/}(6493), 860--868.

\bibitem[\protect\citeauthoryear{Koelle, Martin, Antia, Lopman, and
  Dean}{Koelle et~al.}{2022}]{koelle2022changing}
Koelle, K., M.~A. Martin, R.~Antia, B.~Lopman, and N.~E. Dean (2022).
\newblock {The changing epidemiology of SARS-CoV-2}.
\newblock {\em Science\/}~{\em 375\/}(6585), 1116--1121.

\bibitem[\protect\citeauthoryear{Kraemer, Pybus, Fraser, Cauchemez, Rambaut,
  and Cowling}{Kraemer et~al.}{2021}]{kraemer2021monitoring}
Kraemer, M.~U., O.~G. Pybus, C.~Fraser, S.~Cauchemez, A.~Rambaut, and B.~J.
  Cowling (2021).
\newblock {Monitoring key epidemiological parameters of SARS-CoV-2
  transmission}.
\newblock {\em Nature medicine\/}~{\em 27\/}(11), 1854--1855.

\bibitem[\protect\citeauthoryear{Lavezzo, Franchin, Ciavarella,
  Cuomo-Dannenburg, Barzon, Del~Vecchio, Rossi, Manganelli, Loregian, Navarin,
  et~al.}{Lavezzo et~al.}{2020}]{lavezzo2020suppression}
Lavezzo, E., E.~Franchin, C.~Ciavarella, G.~Cuomo-Dannenburg, L.~Barzon,
  C.~Del~Vecchio, L.~Rossi, R.~Manganelli, A.~Loregian, N.~Navarin, et~al.
  (2020).
\newblock {Suppression of a SARS-CoV-2 outbreak in the Italian municipality of
  Vo’}.
\newblock {\em Nature\/}~{\em 584\/}(7821), 425--429.

\bibitem[\protect\citeauthoryear{Lavine, Bjornstad, and Antia}{Lavine
  et~al.}{2021}]{lavine2021immunological}
Lavine, J.~S., O.~N. Bjornstad, and R.~Antia (2021).
\newblock {Immunological characteristics govern the transition of COVID-19 to
  endemicity}.
\newblock {\em Science\/}~{\em 371\/}(6530), 741--745.

\bibitem[\protect\citeauthoryear{Lloyd-Smith, Schreiber, Kopp, and
  Getz}{Lloyd-Smith et~al.}{2005}]{lloyd2005superspreading}
Lloyd-Smith, J.~O., S.~J. Schreiber, P.~E. Kopp, and W.~M. Getz (2005).
\newblock Superspreading and the effect of individual variation on disease
  emergence.
\newblock {\em Nature\/}~{\em 438\/}(7066), 355--359.

\bibitem[\protect\citeauthoryear{Lopman, Liu, Le~Guillou, Lash, Isakov, and
  Jenness}{Lopman et~al.}{2020}]{lopman2020model}
Lopman, B., C.~Y. Liu, A.~Le~Guillou, T.~L. Lash, A.~P. Isakov, and S.~M.
  Jenness (2020).
\newblock {A model of COVID-19 transmission and control on university
  campuses}.
\newblock {\em MedRxiv\/}.

\bibitem[\protect\citeauthoryear{Metcalf, Morris, and Park}{Metcalf
  et~al.}{2020}]{metcalf2020mathematical}
Metcalf, C. J.~E., D.~H. Morris, and S.~W. Park (2020).
\newblock Mathematical models to guide pandemic response.
\newblock {\em Science\/}~{\em 369\/}(6502), 368--369.

\bibitem[\protect\citeauthoryear{Moreira~Jr, Kitchin, Xu, Dychter, Lockhart,
  Gurtman, Perez, Zerbini, Dever, Jennings, et~al.}{Moreira~Jr
  et~al.}{2022}]{moreira2022safety}
Moreira~Jr, E.~D., N.~Kitchin, X.~Xu, S.~S. Dychter, S.~Lockhart, A.~Gurtman,
  J.~L. Perez, C.~Zerbini, M.~E. Dever, T.~W. Jennings, et~al. (2022).
\newblock Safety and efficacy of a third dose of {BNT162b2} {COVID-19} vaccine.
\newblock {\em New England Journal of Medicine\/}.

\bibitem[\protect\citeauthoryear{Prunas, Warren, Crawford, Gazit, Patalon,
  Weinberger, and Pitzer}{Prunas et~al.}{2022}]{prunas2022vaccination}
Prunas, O., J.~L. Warren, F.~W. Crawford, S.~Gazit, T.~Patalon, D.~M.
  Weinberger, and V.~E. Pitzer (2022).
\newblock {Vaccination with BNT162b2 reduces transmission of SARS-CoV-2 to
  household contacts in Israel}.
\newblock {\em Science\/}, eabl4292.

\bibitem[\protect\citeauthoryear{Saad-Roy, Morris, Metcalf, Mina, Baker,
  Farrar, Holmes, Pybus, Graham, Levin, et~al.}{Saad-Roy
  et~al.}{2021}]{saad2021epidemiological}
Saad-Roy, C.~M., S.~E. Morris, C.~J.~E. Metcalf, M.~J. Mina, R.~E. Baker,
  J.~Farrar, E.~C. Holmes, O.~G. Pybus, A.~L. Graham, S.~A. Levin, et~al.
  (2021).
\newblock {Epidemiological and evolutionary considerations of SARS-CoV-2
  vaccine dosing regimes}.
\newblock {\em Science\/}~{\em 372\/}(6540), 363--370.

\bibitem[\protect\citeauthoryear{Saad-Roy, Wagner, Baker, Morris, Farrar,
  Graham, Levin, Mina, Metcalf, and Grenfell}{Saad-Roy
  et~al.}{2020}]{saad2020immune}
Saad-Roy, C.~M., C.~E. Wagner, R.~E. Baker, S.~E. Morris, J.~Farrar, A.~L.
  Graham, S.~A. Levin, M.~J. Mina, C.~J.~E. Metcalf, and B.~T. Grenfell (2020).
\newblock {Immune life history, vaccination, and the dynamics of SARS-CoV-2
  over the next 5 years}.
\newblock {\em Science\/}~{\em 370\/}(6518), 811--818.

\bibitem[\protect\citeauthoryear{Tan, Chiew, Pang, Lee, Ong, Lye, and Tan}{Tan
  et~al.}{2023}]{tan2023vaccine}
Tan, C.~Y., C.~J. Chiew, D.~Pang, V.~J. Lee, B.~Ong, D.~C. Lye, and K.~B. Tan
  (2023).
\newblock {Vaccine effectiveness against Delta, Omicron BA. 1, and BA. 2 in a
  highly vaccinated Asian setting: a test-negative design study}.
\newblock {\em Clinical Microbiology and Infection\/}~{\em 29\/}(1), 101--106.

\bibitem[\protect\citeauthoryear{Tartof, Slezak, Fischer, Hong, Ackerson,
  Ranasinghe, Frankland, Ogun, Zamparo, Gray, et~al.}{Tartof
  et~al.}{2021}]{tartof2021effectiveness}
Tartof, S.~Y., J.~M. Slezak, H.~Fischer, V.~Hong, B.~K. Ackerson, O.~N.
  Ranasinghe, T.~B. Frankland, O.~A. Ogun, J.~M. Zamparo, S.~Gray, et~al.
  (2021).
\newblock {Effectiveness of mRNA BNT162b2 COVID-19 vaccine up to 6 months in a
  large integrated health system in the USA: a retrospective cohort study}.
\newblock {\em The Lancet\/}~{\em 398\/}(10309), 1407--1416.

\bibitem[\protect\citeauthoryear{Viboud, Bj{\o}rnstad, Smith, Simonsen, Miller,
  and Grenfell}{Viboud et~al.}{2006}]{viboud2006synchrony}
Viboud, C., O.~N. Bj{\o}rnstad, D.~L. Smith, L.~Simonsen, M.~A. Miller, and
  B.~T. Grenfell (2006).
\newblock Synchrony, waves, and spatial hierarchies in the spread of influenza.
\newblock {\em science\/}~{\em 312\/}(5772), 447--451.

\bibitem[\protect\citeauthoryear{Wallinga and Lipsitch}{Wallinga and
  Lipsitch}{2007}]{wallinga2007generation}
Wallinga, J. and M.~Lipsitch (2007).
\newblock How generation intervals shape the relationship between growth rates
  and reproductive numbers.
\newblock {\em Proceedings of the Royal Society B: Biological Sciences\/}~{\em
  274\/}(1609), 599--604.
